---
title: "Sentiment Analysis 1"
author: "Dory Munoko"
date: "12/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The aim of this project is to build a sentiment analysis model which will allow us to categorize words based on their sentiments, that is whether they are positive, negative and also the magnitude of it.

Developing our Sentiment Analysis Model in R
We will carry out sentiment analysis with R in this project. The dataset that we will use will be provided by the R package ‘janeaustenR’.

```{r, results='asis'}
library(tidytext)
library(janeaustenr)
library(dplyr)
library(stringr)
library(tidyr)
library(ggplot2)
library(reshape2)
library(wordcloud)
sentiments
```
We will make use of three general purpose lexicons like –
  a.) AFINN
  b.) bing
  c.) loughran
```{r, results='asis'}
get_sentiments("bing")
```

Performing Sentiment Analysis with the Inner Join
The janeaustenr package- Provides us with the textual data in the form of books authored by the novelist Jane Austen. Tidytext- allows us to perform efficient text analysis on our data.
unnest_tokens() function- to convert the text of our books into a tidy format.
```{r, results='asis'}
tidy <- austen_books() %>%
        group_by(book) %>%
        mutate(linenumber = row_number(),
        chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]", 
                          ignore_case = TRUE)))) %>%
ungroup() %>%
     unnest_tokens(word, text)
```

We will now make use of the “bing” lexicon to and implement filter() over the words that correspond to joy. We will use the book Sense and Sensibility and derive its words to implement out sentiment analysis model.
```{r}
positive_sent <- get_sentiments("bing") %>%
                  filter(sentiment == "positive")

tidy %>%
  filter(book == "Emma") %>%
  semi_join(positive_sent) %>%
  count(word, sort = TRUE)
```
Use spread() function to segregate our data into separate columns of positive and negative sentiments. 
Use the mutate() function to calculate the total sentiment (the difference between positive and negative sentiment).
```{r}
bing <- get_sentiments("bing")
        Emma_sentiment <- tidy %>%
        inner_join(bing) %>%
        count(book = "Emma" , index = linenumber %/% 80, sentiment) %>%
        spread(sentiment, n, fill = 0) %>%
        mutate(sentiment = positive - negative)
```

Visualize the words present in the book “Emma” based on their corresponding positive and negative scores.
```{r}
ggplot(Emma_sentiment, aes(index, sentiment, fill = book)) +
       geom_bar(stat = "identity", show.legend = TRUE) +
       facet_wrap(~book, ncol = 2, scales = "free_x")
```

Counting the most common positive and negative words that are present in the novel.
```{r}
count_words <- tidy %>%
               inner_join(bing) %>%
               count(word, sentiment, sort = TRUE)
               head(count_words)
```

Visualization of our sentiment score.
```{r}
count_words %>%
         filter(n > 200) %>%
         mutate(n = ifelse(sentiment == "negative", -n, n)) %>%
         mutate(word = reorder(word, n)) %>%
ggplot(aes(word, n, fill = sentiment))+
         geom_col() +
         coord_flip() +
         labs(y = "Sentiment Score")
```

Use the comparision.cloud() function to plot both negative and positive words in a single wordcloud.
```{r}
tidy %>%
   inner_join(bing) %>%
   count(word, sentiment, sort = TRUE) %>%
   acast(word ~ sentiment, value.var = "n", fill = 0) %>%
   comparison.cloud(colors = c("red", "dark green"),
          max.words = 200)
```





